\section{Executive Summary}
  David Lachut and Kaustav Lahiri, Department of Computer Science and
Electrical Engineering, University of Maryland, Baltimore County, propose to
the complete the following project between February 27 and May 15, 2013:
  
  ``Rethinking RAM: Testing alternative models of computation'' will examine
  the traditional Random Access Machine (RAM) model of computation and compare
  it to the Virtual Address Translation (VAT) model proposed by Jurkiewicz and
  Mehlhorn in their recent paper ``The cost of address translation''. In their
  paper, the authors contend that the \textit{RAM model}, traditionally used
  for algorithm analysis, yields inaccurate results, because it makes invalid
  assumptions about memory access in a modern computer. 

  Lachut and Lahiri propose to verify the new VAT model experimentally. The
  project will \textit{benchmark} implementations of several algorithms. These
  results will be compared to the predictions of the two \textit{computational
  models}, for the purpose of determining which of the models produces a more
  accurate prediction of algorithmic runtimes.
  
  \paragraph{Intellectual Merit} This project extends the work of previous
  authors in the area of algorithm analysis. The investigators will work to
  determine whether this new model of computation would benefit future
  researchers. The process of reaching the conclusion will require the
  formulation of novel analyses of familiar algorithms, and the development of
  an algorithmic benchmarking system.
  
  \paragraph{Broader Impact} Should the project determine that the VAT model
  is indeed superior to other existing models of computation, the field of
  algorithm analysis will be changed and its predictions will more accurately
  reflect the real state of the world. This will enable better algorithm design
  and help to allow computer scientists to continue advancing information
  technology to meet the needs of society.