\section{Conclusions}
We did the experiment, because reasons. We found a result, and thought it
was pretty nifty.

**************************************************************************************************
Our paper has a focused aim of experimentally verifying the VAT model of algorithmic complexity. Jurkiewicz and Melhorn has come up with an innovative concept of incorporating the costs of virtual address translation[5] in algorithmic complexities, but did not provide enough evidence to support the use of this new model. Thus, an experimental verification was required and we have managed to do that with our findings. Our straightforward verification and benchmarking process will help computer scientists decide whether to shift to this new VAT model or not. Though we experienced some difficulties in the mathematical deduction and we plan to refine our calculations in future, our experimental results can be still be used for decision making. As we continuously analyze and benchmark more algorithms, we will be able to present our personal view on using the VAT model, in our final paper. Should the project determine that the VAT model is indeed superior to other existing models of computation, the field of algorithm analysis will be changed and its predictions will more accurately reflect the real state of the world. This will enable better algorithm design and help to allow computer scientists to continue advancing information technology to meet the needs of the society.
