\section{Motivation}

Analysis of algorithms on abstract machines serves as a crucial element of
computer science, which allows incredible increases in the speed and utility
of computer programs [4]. Until now, computer scientists have used the RAM and
the EM models to perform algorithmic analysis accurately. But Jurkiewicz and
Mehlhorn observe discrepancies with some experimental findings and attempt to
push forward the VAT model to account for these discrepancies [5]. 

Before algorithm analysts shift to this new model, they must carefully verify
its claims and correctness, it's utility. This is where Jurkiewicz and
Mehlhorn's contribution falls short. Their paper mentions that experimental
findings differ with the theoretical predictions of the RAM model and claims
to solve these difficulties with the VAT model, but it does not clearly
present these findings. Further, the number of algorithms studied in the paper
is limited. For these reasons, someone must further test the model and expand
the set of tested and analyzed algorithms, comparing the analysis with
benchmarks, before analysts can incorporate this new model into their work.

More accurate algorithm analysis would help maintain the pace of innovation
enjoyed by computer science for a generation. If it could be verifed by
experimental comparison that the new VAT model be more accurate, then this
would serve as an incentive to researchers to use the proposed model for more
accurate estimations of complexities of algorithms.